A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-06-08 papers/execution-model/APLAS 2021/paper.tex
Add files via upload

\documentclass[a4paper]{llncs}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}
\usepackage{fixme}
\usepackage{xcolor}
\usepackage{listings}
\lstdefinelanguage{michelson}{
%  basicstyle=\ttfamily,
  morekeywords={parameter,storage,or,unit,mutez,pair,bool,address}, sensitive=false,
  morecomment=[l]{\#},
  morecomment=[s]{/*}{*/},
  morestring=[b]",
}
\lstset{language=Caml}
\input{macros}

\title{A Typed Programmatic Interface to Contracts on the Blockchain}

\author{Thi Thu Ha Doan\and
Peter Thiemann\orcidID{0000-0002-9000-1239}}
\institute{University of Freiburg, Germany\\
\email{\{doanha,thiemann\}@informatik.uni-freiburg.de}
}

\date{\today}

\begin{document}
\maketitle
\pagestyle{plain}
\begin{abstract}
  Smart contract applications on the block chain can only reach their full potential if
  they can be integrated with traditional software systems. Invoking
  contracts and observing the state of the blockchain requires a
  programmatic interface. We propose a typed API for this
  purpose and establish some properties of the combined
  system. Specifically, we provide an execution model that
  enables us to prove type-safe interaction between programs and the 
  blockchain. We establish further properties of the model that
  give rise to requirements on the API. A prototype of the interface
  is implemented in OCaml for the Tezos blockchain.
\end{abstract}

\section{Introduction}
\label{sec:introduction}

First generation blockchains were primarily geared towards supporting
cryptocurrencies. The most prominent system of this kind is Bitcoin
\cite{bitcoin-whitepaper}. Though Bitcoin already features a
rudimentary programming language called Script, second generation
blockchains like the Ethereum blockchain \cite{eth-whitepaper} feature
Turing-complete programming facilities, called 
Smart Contracts. They provide robust trustworthy distributed computing
facilities even though the programs run on a peer-to-peer network with
untrusted participants. Each peer in the network runs the same program
and uses cryptographic methods to check the results among the other
peers and to create a persistent ledger of all transactions, the
blockchain, thus ensuring the integrity of the results. Third
generation blockchains, like Tezos \cite{tezos-whitepaper}, are even adaptable to
new requirements without breaking participating peers (no ``hard
forks'' required).

@@

Suppose you want to run an auction on the blockchain using a smart
contract. Once to the contract is deployed, the
auction is open for bidding, but it should be closed after 48 hours,
say. Such a timeout is a typical task for an oracle. Rather than
trusting a generic oracle, you prefer to roll your own mechanism that reliably closes the auction
after 48 hours have passed. So you want to write a program to do so.

@@

Neither task can be implemented as a smart contract alone because both react
to external triggers. Closing requires to schedule the invocation of a
contract at a certain time. Bidding 
requires to watch the current highest bid of the contract and
react if another bidder places a higher bid.

@@

In Tezos, there are two types of accounts: implicit accounts, which are associated with a pair of private/public keys, and smart contracts, which are a programmable account created by an origination operation and have no corresponding secret key. The address of a smart contract is a unique public hash that depends on the creation operation. An implicit account is maintained on the blockchain with its public key, balance, and counter, whose job is to prevent replay attacks. A smart contract account is stored with its script, storage, and balance. A contract script maps a pair of a parameter and a storage, which have fixed and monomorphic types to a pair of a list of internal operations and an updated storage. An implicit account performs three kinds of transactions: (1) transfer tokens to another implicit account, (2) invoke a smart contract, or (3) originate a new smart contract. A contract origination specifies the script of the contract and the initial contents of the contract storage, while a contract invocation must provide input data. Each transaction contains a fee to be paid either by payment to a baker or by destruction (burning). A transaction is injected into the blockchain network via a node, which then validates the transaction before submitting it to the network. Generally, a transaction can be rejected by the node for a number of reasons. Once the transaction is valid, it is injected into the mempool, which contains all pending transactions before they can be included in a block. On the other hand, a pending transaction can be lost in the mempool. A transaction is timed out when 60 blocks have passed and it can no longer be included in a block. When a transaction is included in a blockchain, the related accounts are updated according to the transaction result.

The execution model is an abstraction of the Tezos blockchain \cite{tezos-whitepaper}
augmented with functional (OCaml) programs that interact with the
blockchain. As the blockchain is realized by a peer-to-peer network of
independent nodes, interaction happens through
\emph{local nodes} that receive requests to originate and invoke
contracts from programs that run on a particular node. We model the blockchain
itself as a separate, abstract global entity that represents the
current consensual state of the system. Our model does not express
low-level details, but relies on nondeterminism to describe
the possible behaviors of the system. In particular, we do
\textbf{not} formalize the execution of the smart contracts
themselves, we rather consider them as black boxes that execute in a
safe-safe way. Tezos' smart contract language Michelson and its
properties have been formalized elsewhere \cite{DBLP:conf/fm/BernardoCHPT19}.

@@

\newpage{}

@@

\newpage{}
\appendix

\section{Unused}
\label{sec:unused}

\subsection{An Implicit Account Transfer}

\begin{mathpar}
  \inferrule[rejected of public key]{
    \NEG\ \CHECKPUB (\BLOCKCHAIN.\MANAGERS, \PUK') \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
    } \SystemTrans
   { [\EC{\RAISE\ \ERRPUK} :: \EXPRS, \ACCOUNTS] \|
     \BLOCKCHAIN
    }
  }
\end{mathpar}

\begin{mathpar}
  \inferrule[rejected of fee]{
    \NEG\ \CHECKGAS (\BLOCKCHAIN.\MANAGERS, \PUK,\PUK',\NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
    { [\EC\OP :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
     } \SystemTrans
    { [\EC{\RAISE\ \ERRFEE} :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
    }
  }
\end{mathpar}
\begin{mathpar}
  \inferrule[rejected of counter]{
    \NEG\ \CHECKCOU (\BLOCKCHAIN.\MANAGERS, \OP.\PUK) \\
    }{
    { [\EC\OP  :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
    }
    \SystemTrans
    { [\EC{\RAISE\ \ERRCOUNT} :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
   }
  }
\end{mathpar}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse 
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME < 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans  \\
    {[\PENDING, \Angle{\OP,\OPH, \TIME,\TIME'} :: \ACCEPTED,
      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
      \CONTRACTORS, \TIME'+1]}
  }
\end{mathpar}
Rule 7 [timeout]: (applies to both, implicit transfers and contract invocations)
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
    \TIME'-\TIME \ge 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans
    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \OP.\PUK, \FALSE),
      \CONTRACTORS, \TIME']}
  }
\end{mathpar}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Contracts}
\label{sec:contracts}

\begin{mathpar}
  \inferrule[rejected of code]{
    \NEG\ \CHECKPRG (\CODE) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN \to 
    [\EXPRS[\RAISE\ \ERRPRG] :: \EXPRS, \ACCOUNTS] \|
     \BLOCKCHAIN
  }
\end{mathpar}

\iffalse 
Rule 3 [rejected of counter]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKCOU (\BLOCKCHAIN.\MANAGERS, \PUK) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN \to 
    [\EXPRS[\RAISE\ \ERRCOUNT] :: \EXPRS, \ACCOUNTS] \|
     \BLOCKCHAIN
  }
\end{mathpar}

\begin{mathpar}
  \inferrule[rejected of balance]{
    \NEG\ \CHECKBAL (\BLOCKCHAIN.\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN \to 
    [\EXPRS[\RAISE\ \ERRBAL] :: \EXPRS, \ACCOUNTS] \|
     \BLOCKCHAIN
  }
\end{mathpar}
\fi

\begin{mathpar}
  \inferrule[rejected of fee]{
    \NEG\ \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN \to 
    [\EXPRS[\RAISE\ \ERRFEE] :: \EXPRS, \ACCOUNTS] \|
     \BLOCKCHAIN
  }
\end{mathpar}

\begin{mathpar}
  \inferrule[rejected of initial storage]{
    \NEG\ \CHECKINIT (\CODE, \INIT) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN \to 
    [\EXPRS[\RAISE\ \ERRINIT] :: \EXPRS, \ACCOUNTS] \|
     \BLOCKCHAIN
  }
\end{mathpar}

% \begin{mathpar}
%   \inferrule[Block-Timeout]{
%     %\OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
%     \TIME-\hat\TIME > 60
% }{
%       [ \OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING}
%      ::\PENDING, \MANAGERS,
%       \CONTRACTORS, \TIME]  
%       \BlockTrans \\    
%       [ \OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSTIMEOUT}
%      :: \PENDING, \UPDATECOU(\MANAGERS, \OP.\PUK, \FALSE),
%       \CONTRACTORS, \TIME] 
%   }

% \end{mathpar}
~\\
~\\
B. \textbf{Transfer}

\begin{mathpar}
  \inferrule[Block-Call]{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\ 
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUH (\CONTRACTORS, \PUH) \\
    \CHECKARG (\CONTRACTORS, \PUH, \PARAMETER) \\
    \CHECKGAS (\CONTRACTORS, \PUH, \PARAMETER, \MTEZ) \\
%    \OPH = \GENERATEOPH (\PUK,\PUH, \PARAMETER,\NTEZ, \MTEZ, \TIME) \\
    \OPH = \GENERATEOPH (\OP, \TIME) \\
    \OP =  \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\    
  }{ [\EC\OP  :: \EXPRS, \ACCOUNTS,
      ] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]     
    \SystemTrans \\
    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \|
      [\OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING}
     :: \PENDING, \UPDATECOU(\MANAGERS, \PUK, \TRUE), \CONTRACTORS, \TIME]}
\end{mathpar}

\iffalse 
Rule 2 [rejected of counter]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKCOU (\BLOCKCHAIN.\MANAGERS, \PUK) \\
    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
  }{[\EC\OP :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN      
    \SystemTrans
   [\EC[\RAISE\ \ERRCOUNT] :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN }
\end{mathpar}
~\\
~\\
Rule 3 [rejected of balance]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ \\
  }{[\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]      
    \SystemTrans
    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
\end{mathpar}
\fi

\begin{mathpar}
  \inferrule[rejected of public hash]{
    \NEG\ \CHECKPUH (\BLOCKCHAIN.\CONTRACTORS, \PUH) \\
    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ
  }{[\EC\OP  :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN    
    \SystemTrans
    [\EXPRS[\RAISE\ \ERRPUH], \ACCOUNTS] \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
  \inferrule[rejected of argument]{
    \NEG\ \CHECKARG (\BLOCKCHAIN.\CONTRACTORS, \PUH, \PARAMETER)\\
    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ
  }{[\EC\OP  :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN    
    \SystemTrans
    [\EXPRS[\RAISE\ \ERRARG], \ACCOUNTS] \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
  \inferrule[rejected of fee]{
    \NEG\ \CHECKGAS (\BLOCKCHAIN.\CONTRACTORS, \PUH, \PARAMETER, \MTEZ) \\ \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK{\PUH}\MTEZ 
  }{[\EC\OP  :: \EXPRS, \ACCOUNTS] \| \BLOCKCHAIN    
    \SystemTrans
    [\EXPRS[\RAISE\ \ERRFEE], \ACCOUNTS] \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
  \inferrule[block Accept]{
    \OP = \TRANSFER[\PARAMETER]\NTEZ\PUK\PUH\MTEZ \\
    \TIME-\hat\TIME \le 60
  }{
    [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING} :: \PENDING, \MANAGERS,
    \CONTRACTORS, \TIME]
    \BlockTrans \\
    [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, 
    \UPDATESUCC (\MANAGERS, \PUK, '', \NTEZ, \MTEZ), \\
    \UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \PARAMETER),
    \TIME+1]
  }
\end{mathpar}

\subsection{Queries}
\label{sec:queries-1}

\begin{mathpar}
  \inferrule[counter]{
    \BLOCKSYSTEM = 
      [\PENDING, \PUK \mapsto \Angle{\BAL, \COU} :: \MANAGERS, \CONTRACTORS, \TIME]
  }{[\EC{\GETCOUNTER\PUK} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \SystemTrans\ [\EC{\COU} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
\inferrule[balance of smart contract]{
    \BLOCKSYSTEM = 
      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
  }{[\EC{\GETBALANCE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \SystemTrans\ [\EC{\BAL} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
  \inferrule[storage]{
    \BLOCKSYSTEM = 
      [\PENDING, \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
  }{[\EC{\GETSTORAGE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \SystemTrans\ [\EC{\STORAGE} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
  \inferrule[code]{
    \BLOCKSYSTEM = 
      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
  }{[\EC{\GETCODE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \SystemTrans\ [\EC{\CODE} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
  \inferrule[type]{
    \BLOCKSYSTEM = 
      [\PENDING,  \MANAGERS, \PUH \mapsto \Angle{\CODE, \TIME, \BAL, \STORAGE} :: \CONTRACTORS, \TIME]
  }{[\EC{\GETTYPE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \SystemTrans\ [\EC{\Delta (\PUH)} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
  \inferrule[fail of a query for an implicit account]{
    \NEG\ \CHECKPUB (\BLOCKCHAIN.\MANAGERS, \PUK) \
  }{[\EC{\GETBALANCE\PUK/\GETCOUNTER\PUK} :: \EXPRS, \ACCOUNTS]  \| 
  \BLOCKCHAIN 
    \SystemTrans {[\EC{\RAISE\ \ERRPUK} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}}
\end{mathpar}

\begin{mathpar}
  \inferrule[fail of a query for a smart contract]{
    \NEG\ \CHECKPUH (\BLOCKCHAIN.\CONTRACTORS, \PUH) 
  }{[\EC{\GETBALANCE\PUH/\GETSTORAGE\PUH/\GETCODE\PUH/\GETTYPE\PUH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \SystemTrans\\ [\EC{\RAISE\ \ERRPUH} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
  \inferrule[status-pending]{
    \BLOCKSYSTEM = 
      [\OPH \mapsto \Angle{\OP, \TIME, \STATUSPENDING} :: \PENDING,  \CONTRACTORS, \TIME]
  }{[\EC{\GETSTATUS\OPH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \SystemTrans\ [\EC{\STATUSPENDING} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
  \inferrule[status-including]{
    \BLOCKSYSTEM = 
      [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME'} :: \PENDING,  \CONTRACTORS, \TIME] \\
    $n$ \ = \TIME\ - \TIME'
  }{[\EC{\GETSTATUS\OPH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \SystemTrans\ [\EC{\STATUSINCLUDING($n$)} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

\begin{mathpar}
  \inferrule[status-timeout]{ 
   \BLOCKSYSTEM = 
      [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSTIMEOUT} :: \PENDING, \CONTRACTORS, \TIME]
  }{[\EC{\GETSTATUS\OPH} :: \EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN
    \SystemTrans\ [\EC{\STATUSTIMEOUT} ::\EXPRS, \ACCOUNTS]  \| \BLOCKCHAIN}
\end{mathpar}

\subsection{Functions}
\label{sec:functions}

\begin{enumerate}
    \item Function $\CHECKPUB(\MANAGERS, \PUK)$ checks whether a public key $\PUK$ exists in $\MANAGERS$.
    \begin{itemize}
    \item[] $\CHECKPUB(\MANAGERS, \PUK)$ = $\TRUE$ iff $\PUK \in \DOM(\MANAGERS)$
    \end{itemize}
    \item Function $\CHECKPUH(\CONTRACTORS, \PUH)$ checks whether a public hash $\PUH$ exists in $\CONTRACTORS$.
     \begin{itemize}
    \item[] $\CHECKPUH(\CONTRACTORS, \PUH)$ = $\TRUE$ iff $\PUH \in \DOM(\CONTRACTORS)$
    \end{itemize}
    \item Function $\CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ)$ checks whether the balance of the account that associates with the public key $\PUK$ is greater or equal to $\NTEZ$ plus $\MTEZ$.
    \begin{itemize}
    \item[] $\MANAGERS(\PUK)$ = $\Angle{\BAL, \COU}$ and $\BAL \ge \NTEZ + \MTEZ$
    \end{itemize}
    \item Function $\CHECKCOU (\MANAGERS, \PUK)$ checks whether the current counter of an account that associates with the public key $\PUK$ is unlocked (its flag is False).
    \begin{itemize}
    \item[] $\MANAGERS(\PUK)$ = $\Angle{\BAL, \COU}$ and $\COU.b = \FALSE$
    \end{itemize}
   % \item Function \CHECKEXIST (\OPH, \PENDING, \ACCEPTED)\ checks whether an operation  \OPH\ exists in either \PENDING\ or \ACCEPTED.
    \item Function $\UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ)$ updates the balance and the counter of the account that associates with the public key $\PUK$ and the balance of the account that associates with the public key $\PUK'$, where
    \begin{itemize}
        \item[]  $\PUK \mapsto \Angle{\BAL, (\hat\NTEZ, \TRUE)}$ $\Rightarrow$ $ \PUK \mapsto \Angle{\BAL - \NTEZ - \MTEZ, (\hat\NTEZ + 1, \FALSE)}$     
        \item[] $\PUK' \mapsto \langle  \BAL', \COU' \rangle$ $\Rightarrow$ $\PUK' \mapsto \langle \BAL' + \NTEZ, \COU' \rangle $         
    \end{itemize}

    \item Function $\UPDATECOU(\MANAGERS, \PUK, \BOOLEAN)$ updates the counter flag (True $=$ locked, False $=$ unlocked) of the account that associates with the public key $\PUK$, where
    \begin{itemize}
        \item[]  $ \PUK \mapsto \langle \BAL, (\NTEZ, \hat\BOOLEAN) \rangle $ $\Rightarrow$ $\PUK \mapsto \langle \BAL, (\NTEZ, \BOOLEAN) \rangle $ 
    \end{itemize}

    \item Function  $\UPDATECONSTR (\CONTRACTORS, \PUH, \NTEZ, \PARAMETER)$ updates the contractor that associates with the public hash $\PUH$, where
    \begin{itemize}
        \item[] $\PUH  \mapsto \langle   \CODE, \TIME, \BAL, \STORAGE, \rangle $ $\Rightarrow$ $\PUH  \mapsto \langle  \BAL + \NTEZ, \CODE, \\ \UPDATESTORAGE(\STORAGE,\CODE,\PARAMETER) \rangle $
    \end{itemize}

     \item Function $\UPDATESTORAGE(\STORAGE, \CODE,  \PARAMETER)$ returns the new storage by running the code $\CODE$ on the  current storage  $\STORAGE$ with  the input parameter $\PARAMETER$.

    \item Function $\CHECKPRG (\CODE)$ checks whether the code $\CODE$ is well type.

    \begin{itemize}
        \item[] $\CHECKPRG (\CODE) = \TRUE$ iff $\CODE : \TPAIR\ \TYPE_p\ \TYPE_s$
    \end{itemize}
    \item Function $\CHECKINIT (\CODE, \INIT)$ checks whether the initil stogare valude is well type with corresponding to the code $\CODE$.
    \begin{itemize}
        \item[] $\CHECKINIT (\CODE, \INIT) = \TRUE$ iff $\CODE : \TPAIR\ \TYPE_p\ \TYPE_s$ and $\STRING : \TYPE_s$
    \end{itemize}

    \item Function $\CHECKARG (\CONTRACTORS, \PUH, \PARAMETER)$ checks whether the input parameter  $\PARAMETER$ to the smart contract $\PUH$ in $\CONTRACTORS$ is well type with corresponding to its code.
    \begin{itemize}
        \item[] $\CHECKARG (\CONTRACTORS, \PUH, \PARAMETER) = \TRUE$ iff $\Delta (\PUH) =
  \TPAIR\ \TYPE_p\ \TYPE_s$ and $\PARAMETER : \TYPE_p$
    \end{itemize}

   % \item Function \CHECKGAS(\CODE, \INIT, \MTEZ) checks whether the gas that is consumed to run the code \CODE\ for the initial value \INIT\ is less or equal to \MTEZ.
    \item Function  $\CHECKGAS (\MANAGERS, \PUK,\NTEZ, \MTEZ)$/ $\CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ)$ / $\CHECKGAS (\CONTRACTORS, \PUH, \PARAMETER, \MTEZ)$ check whether the fee that is consumed to emit the opertion is less or equal to the fee \MTEZ. 
    %run the code \CODE\ that associates with the public hash \PUH\ for the paremeter \PARAMETER\ is less or equal to \MTEZ.
    \item Function \GENERATEOPH (\PUK, {\ADDR /\CODE},{\INIT /\PARAMETER}, \NTEZ, \MTEZ,  \TIME) generates an operation hash.

    \item Function \GENERATEHASH (\CODE, \TIME)  generates the public hash of a smart contract.
    \end{enumerate}

@@

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}
\usepackage{fixme}
\usepackage{xcolor}
\usepackage{listings}
\lstdefinelanguage{michelson}{
%  basicstyle=\ttfamily,
  morekeywords={parameter,storage,or,unit,mutez,pair,bool,address}, sensitive=false,
  morecomment=[l]{\#},
  morecomment=[s]{/*}{*/},
  morestring=[b]",
}
\lstset{language=Caml}
\input{macros}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{A Typed Programmatic Interface to Contracts on the Blockchain}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and
Peter Thiemann\orcidID{0000-0002-9000-1239}}

%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Freiburg, Germany \\
\email{\{doanha,thiemann\}@informatik.uni-freiburg.de}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  Smart contract applications on the block chain can only reach their full potential if
  they can be integrated with traditional software systems. Invoking
  contracts and observing the state of the blockchain requires a
  programmatic interface. We propose a typed API for this
  purpose and establish some properties of the combined
  system. Specifically, we provide an execution model that
  enables us to prove type-safe interaction between programs and the 
  blockchain. We establish further properties of the model that
  give rise to requirements on the API. A prototype of the interface
  is implemented in OCaml for the Tezos blockchain.

\keywords{smart contract  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}
\label{sec:introduction}
First generation blockchains were primarily geared towards supporting
cryptocurrencies. The most prominent system of this kind is Bitcoin
\cite{bitcoin-whitepaper}. Though Bitcoin already features a
rudimentary programming language called Script, second generation
blockchains like the Ethereum blockchain \cite{eth-whitepaper} feature
Turing-complete programming facilities, called 
Smart Contracts. They provide robust trustworthy distributed computing
facilities even though the programs run on a peer-to-peer network with
untrusted participants. Each peer in the network runs the same program
and uses cryptographic methods to check the results among the other
peers and to create a persistent ledger of all transactions, the
blockchain, thus ensuring the integrity of the results. Third
generation blockchains, like Tezos \cite{tezos-whitepaper}, are even adaptable to
new requirements without breaking participating peers (no ``hard
forks'' required).

@@

Suppose you want to run an auction on the blockchain using a smart
contract. Once to the contract is deployed, the
auction is open for bidding, but it should be closed after 48 hours. Such a timeout is a typical task for an oracle. Rather than
trusting a generic oracle, you prefer to roll your own mechanism that reliably closes the auction
after 48 hours have passed. So you want to write a program to do so.

@@

Neither task can be implemented as a smart contract alone because both react
to external triggers. Closing require scheduling the invocation of a
contract at a certain time. Bidding 
requires watching the current highest bid of the contract and
react if another bidder places a higher bid.

@@

In Tezos, there are two types of accounts: implicit accounts, which are associated with a pair of private/public keys, and smart contracts, which are programmable accounts created by an origination operation and have no corresponding secret key. The address of a smart contract is a unique public hash that depends on the creation operation. An implicit account is maintained on the blockchain with its public key, balance, and counter, whose job is to prevent replay attacks. A smart contract account is stored with its script, storage, and balance. A contract script maps a pair of a parameter and a storage, which have fixed and monomorphic types to a pair of a list of internal operations and an updated storage. An implicit account performs three kinds of transactions: (1) transfer tokens to another implicit account, (2) invoke a smart contract, or (3) originate a new smart contract. A contract origination specifies the script of the contract and the initial contents of the contract storage, while a contract invocation must provide input data. Each transaction contains a fee to be paid either by payment to a baker or by destruction (burning). A transaction is injected into the blockchain network via a node, which then validates the transaction before submitting it to the network. Generally, a transaction can be rejected by the node for a number of reasons. Once the transaction is valid, it is injected into the mempool, which contains all pending transactions before they can be included in a block. On the other hand, a pending transaction can be lost in the mempool. A transaction is timed out when 60 blocks have passed and it can no longer be included in a block. When a transaction is included in a blockchain, the related accounts are updated according to the transaction result.

The execution model is an abstraction of the Tezos blockchain \cite{tezos-whitepaper}
augmented with functional (OCaml) programs that interact with the
blockchain. As the blockchain is realized by a peer-to-peer network of
independent nodes, interaction happens through
\emph{local nodes} that receive requests to originate and invoke
contracts from programs that run on a particular node. We model the blockchain
itself as a separate, abstract global entity that represents the
current consensual state of the system. Our model does not express
low-level details, but relies on nondeterminism to describe
the possible behaviors of the system. In particular, we do
\textbf{not} formalize the execution of the smart contracts
themselves, we rather consider them as black boxes that execute in a
safe way. Tezos' smart contract language Michelson and its
properties have been formalized elsewhere \cite{DBLP:conf/fm/BernardoCHPT19}.

@@

@@

@@

\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).
